\documentclass{resume} 
\usepackage[left=0.6in,top=0.35in,right=0.6in,bottom=0.35in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[hidelinks]{hyperref}

\name{Victor Magnani} 
\address{(+34) 681 138048 \\ victor.magnaniramos@gmail.com \\ github.com/Ardet696/ \\ linkedin.com/in/victormagnani}

\begin{document}
\title{Curriculum Vitae}

\vspace{0.3em}
{\small I am currently open to part-time internship opportunities during the academic year or full-time summer internships, and eager to join motivated teams where I can contribute and keep growing.}
\vspace{0.2em}

%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

\begin{rSubsection}{La Salle BCN (Universitat Ramon Llull) -- B.Sc. International Computer Engineering}{Sep 2022 -- Jun 2027}{}{}
  \item ABET-accredited program in English. Software: OOP, Relational Databases, UI/UX (Figma), Git, UML.
  \item Engineering Core: Networking, Data Structures \& Algorithms, FPGA, 8-bit CPU systems, PIC18, ASM/C.
  \item Honors in Ethics (Thought \& Creativity 2).
\end{rSubsection}

\begin{rSubsection}{Collegi Sagrat Cor -- Science and Technology Baccalaureate}{Sep 2020 -- Jun 2022}{}{}
  \item Mathematics, physics, economics and engineering foundations. High Distinction for research project on asset management and trading strategies for retail traders.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

\begin{rSubsection}{Samsung Galaxy -- Retailer}{Sept 2025}{}{}
    \item Demonstrated product features to customers; developed communication and client-facing skills.
\end{rSubsection}

\begin{rSubsection}{CaixaBank -- Bank Meeter}{Aug 2025}{}{}
  \item Resolved customer inquiries across transactions and digital banking. Assisted senior asset managers with KYC compliance and income source investigation.
\end{rSubsection}

\begin{rSubsection}{Freelance -- Math Tutor}{2022 -- 2023}{}{}
  \item Taught calculus and algebra fundamentals using varied methods to improve student retention.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   PROJECTS
%----------------------------------------------------------------------------------------
\begin{rSection}{Personal Projects}

\begin{rSubsection}{MP3 TUI: Minimalist C++ Winamp-style Mp3 Player}{Jan 2026 -- Present}{}{}
\item Designed a lock-free SPSC RingBuffer feeding SDL's real-time audio callback without mutex contention or glitches.
\item Managed 5 concurrent threads (decode, audio, TUI, pre-warm, auto-advance) with C++20 \texttt{std::jthread}; exception-safe lifecycle via RAII.
\item Built TUI with FTXTUI; contributed new features upstream to the library repository.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   ADDITIONAL
%----------------------------------------------------------------------------------------
\begin{rSection}{Additional}
  \item \textbf{Languages:} English [C1] | Native: Spanish, Catalan, Italian, Currently learning German [A1]
  \item \textbf{Certifications:} CISCO Intro to Networks, Cambridge C1, SIT Study Tour 2024 \quad \textbf{Kaggle:} Python, Intro to ML, Pandas
  \item \textbf{Volunteering:} Built a static website for an HR company; contributed new features to a 10k+ star open-source repository (FTXTUI); Affiliate Member of the Royal Aeronautical Society.
\end{rSection}

\vspace{0.4em}
{\small I actively seek environments where I can be challenged, learn continuously, and contribute meaningfully. I am product-oriented but also love the technical details of how systems work under the hood. Lately I have started deepening my understanding of Linux, computer architecture and low-latency systems — topics I find endlessly fascinating and practically important.}

\end{document}
